\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2022-10-30 Latex/paper.tex
# Some modifications to estimate D_s_x_T_a

\begin{equation}
L_{E}(t_0,t_1,t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) + \int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s.
\end{equation} 
Therefore, if we take $\mathbb{E}^{\mathbb{Q}^{t2}}(\cdot)$ in the last equation, then we get
\begin{equation*}
CA(t, t_0, t_1, t_2) = - \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s \right).
\end{equation*}
From (\ref{ois_forward_rate_curve}) and since $f_{ois}(t,T)$ is a $\mathbb{Q}^{T}$ martingale, we have that
\begin{equation*}
dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,T) dt. 
\end{equation*}
Therefore, if we apply Girsanov's theorem to switch to measure $\mathbb{Q}^{t_2}$, we get that
\begin{equation}\label{ca_general_future}
CA(t, t_0, t_1, t_2) = \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) \nu(s,t_2) ds \right)
\end{equation}
where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}). Now, from the definition of $L_{E}(t,T)$ we have that
\begin{equation*}
D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)} D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right). 
\end{equation*}
If we use the representation formula (\ref{bond_ois}) we get that
\begin{equation*}
D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) = \frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}
\end{equation*}
therefore
\begin{equation}\label{malliavin_derive_L}
D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}. 
\end{equation}
From (\ref{short_rate_cheyette}) y we define $\beta(s,t, x, y) = \exp\left(-\int_{s}^{t} k_{u} \right) \eta(s, x, y)$ we have that
\begin{equation}\label{malliavin_derive_x}
D_s x_{t_0} = \beta(s,t_0, x_s, y_s)M(s,t_0)
\end{equation}
where $M(s,t_0)=\exp\left(-\frac{\int_{s}^{t_0} \left(\partial_x \beta(u,t_0,x_s,y_s)\right)^{2} du}{2} + \int_{s}^{t_0} \partial_x \beta(u,t_0,x_s,y_s) dW^{\mathbb{Q}}_u \right)$. 
Then, we have that
\begin{align*}
D_s L_{E}(t_0,t_1,t_2) &= \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} \beta(s,t_0, x_s, y_s)M(s,t_0) \nonumber \\
\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)} \right)\beta(s,t_0, x_s, y_s)M(s,t_0).
\end{align*}
It is a common practice, freeze the state variables of the model to achieve some approximations. We can approximate $x_s$ and $y_s$ the next way
\begin{align*}
x_s &\approx x_0 \nonumber \\
y_s &\approx y_0 + \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du
\end{align*}
Therefore, 
\begin{equation}\label{approximation_clarkocone}
\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right)\beta(s,t_0, x_0, \hat{y}_s)
\end{equation}
where $\hat{y}_s = y_0 + \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du$.
Now, from (\ref{ca_general_future}) and (\ref{approximation_clarkocone}) we have the next approximation for the convexity adjustmet for future

\hspace{1cm}
\fboxsep1em
\fbox{\parbox{435pt}
{
\begin{equation}\label{ca_approximation_futures}
CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) \int_{0}^{t_0}  \beta(s,t_0, x_0, \hat{y}_s) \nu(s,t_2) ds. 
\end{equation}
}}
\begin{example}\label{example_ca_future}
Let us to set 
\begin{align*}
g(T) &= \exp(-kT) \\
h(t) &= \sigma
\end{align*}
\end{example}
With this parametrization, the Cheyette model is equiavalent to Hull-White model. It is easy to show that under this parametrization, the convexity adjustment (\ref{ca_approximation_futures}) is
\begin{align*}
CA(t_0,t_1) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
\end{align*}
In the next figure, we can check the accuracy of the last formula versus montecarlo. The parameters that we have used are $\sigma=0.015$, $k=0.003$ and flat curve with level $r=0.01$.

@@

\subsection{OIS futures}
In this we will derive the covexity adjustment for overnight-indexed swap (OIS) under. We will define for $t_0 < t_1$
\begin{align*}
R(t_0,t_1) &= \frac{\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1}{t_1 - t_0} \\
R_{avg}(t_0,t_1) &= \frac{\int_{t_0}^{t_1}r_{ois,u} du}{t_1 - t_0}.
\end{align*}
We must observe, that both $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictible and they are only observable in $t_1$. However, since
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$, we can considerer the expected value under the measure $\mathbb{Q}^{t_1}$ that will observable during whole period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales  
\begin{align*} 
\bar{R}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R(t_0,t_1)  \right) \\
\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
\end{align*}
We must do several obeservations. The first observation is that
\begin{align*}
F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1}{t_1 - t_0}, \quad t \in [0,t_0] \\
F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{1}{t_1 - t_0} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
\end{align*}
The can define the convexity adjustment for $ R(t_0,t_1)$ the next way
\begin{equation}\label{R_ois_ca}
CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1) 
\end{equation}
The second observation, is that under the dyam we must do is that
\begin{equation}\label{R_ois_avg}
\mathbb{E}_{t}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}_t^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  
\end{equation}
In order to compute $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1\right)$, we will define
\begin{equation*}
I(t_0,t_1) = \int_{t_0}^{t_1} r_s ds
\end{equation*}
then for $t < t_0$ from (\ref{clark-okone}) and (\ref{malliavin_derive_x}), we have the next representation for $I(t_0,t_1)$
\begin{align}\label{apprx_I_t0_t1}
I(t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) M(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
&\approx \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\hat{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
&= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1} g(s)h(s,x_0,\hat{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
\end{align}
Therefore, we can get the next approximation
\begin{align*}
1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}^{t_1}}\left(R(t_0,t_1)\right) &= \mathbb{E}^{\mathbb{Q}^{t_1}}\left( \exp(I(t_0,t_1)) \right)\\
&= \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)  \mathbb{E}^{\mathbb{Q}^{t_1}}\left(\exp\left(\int_{0}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right)
\end{align*}
where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,\hat{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$. Now, from the Girsanov's theorem we get that
\begin{equation*}
1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{0}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right)
\end{equation*}
Therefore we have that

@@

\subsection{FRAs in arrears}
The cash flows associated to a FRAs in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$. Therefore the payment will be
\begin{equation}
P_{E}(0,t_1)\mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}(t_1,t_1,t_2\right).
\end{equation}
The expected value is clearly taken with respect to the wrong martingale, because $L_{E}(t,t_1,t_2)$ is martingale under the measure $\mathbb{Q}^{t_2}$. In order to calculate, the convexity adjustment we will use as before Clark-Ocone to get a representation for $L_{E}(t_1,t_1,t_2)$ i.e
\begin{equation}\label{general_convexity_fras}
L_{E}(t_1,t_1,t_2) = \mathbb{E}^{\mathbb{Q}^{t_2}}\left(L_{E}(t_1,t_1,t_2) \right) + \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}
\end{equation}
The if we suppose the HJM dynamic (\ref{estimation_forward_rate_curve})and we take $\mathbb{E}^{^{\mathbb{Q}^{t_1}}}(\cdot)$ we get
\begin{align*}
\mathbb{E}^{\mathbb{Q}^{t_1}}\left(L_{E}(t_1,t_1,t_2) \right) &= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}\right)\\
&= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) (\nu(s,t_2)-\nu(s,t_1)) ds \right)
\end{align*}
Where we have used that 
\begin{equation*}
dW^{\mathbb{Q}^{t_2}}_s = dW^{\mathbb{Q}^{t_1}}_s + (\nu(s,t_2) - \nu(s,t_1)) ds 
\end{equation*}
Now from (\ref{malliavin_derive_x}) we have that 
\begin{equation*}
D_s L(t_1,t_1,t_2) = \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1} \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, x_0, \hat{y}_s)M(s,t_1)
\end{equation*}
Therefore, if we define 
\begin{equation*}
CA(t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}\left(t_1,t_1,t_2\right)\right) - L_{E}\left(0,t_1,t_2\right)
\end{equation*}
and we use the last approximation and (\ref{general_convexity_fras}), we can get the next approximation for $CA(t_0,t_1)$ 
\hspace{2cm}
\fboxsep1em
\fbox{\parbox{435pt}
{
\begin{equation}\label{ca_approximations_fra_arrears}
CA(t_0,t_1) \approx  \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \int_{0}^{t_1} \beta(s,t_1, x_0, \hat{y}_s) (\nu(s,t_2) - \nu(s,t_1)) ds.
\end{equation}
}}
\begin{example}
To check how works the last approximation. We will restrict a Hull-White model with mean reversion and volatility constant. We will use are $\sigma=0.1$, $k=0.007$ for our model. The analytical approximation that we get from (\ref{ca_approximation_futures}) is
\begin{equation*}
CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \exp(- k(t_1 + u)) -   \exp(- k(t_2 + u)) du 
\end{equation*}
We have checked the last approximation using MC method to compute the value of a FRA in arrears. We will show the result of the simulation in the next figure

>>>>

\begin{equation}
L_{E}(t_0,t_1,t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) + \int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s.
\end{equation} 
Therefore, if we take $\mathbb{E}^{\mathbb{Q}^{t2}}(\cdot)$ in the last equation, then we get
\begin{equation*}
CA(t, t_0, t_1, t_2) = - \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s \right).
\end{equation*}
From (\ref{ois_forward_rate_curve}) and since $f_{ois}(t,T)$ is a $\mathbb{Q}^{T}$ martingale, we have that
\begin{equation*}
dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,T_2) dt. 
\end{equation*}
Therefore, if we apply Girsanov's theorem to switch to measure $\mathbb{Q}^{t_2}$, we get that
\begin{equation}\label{ca_general_future}
CA(t, t_0, t_1, t_2) = \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) \nu(s,t_2) ds \right)
\end{equation}
where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}). Now, from the definition of $L_{E}(t,T)$ we have that
\begin{equation*}
D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)} D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right). 
\end{equation*}
If we use the representation formula (\ref{bond_ois}) we get that
\begin{equation*}
D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) = \frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}
\end{equation*}
therefore
\begin{equation}\label{malliavin_derive_L}
D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}. 
\end{equation}
Now from (\ref{approximation_D_s_x_t}) with $T_a=t_0$ and $\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y)$ we have that
\begin{align*}
D_s L_{E}(t_0,t_1,t_2) &\approx \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} \beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0) \nonumber \\
\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)} \right)\beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0)
\end{align*}
and therefore
\begin{equation}\label{approximation_clarkocone}
\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right)\beta(t,t_0,x_0,\bar{y}_s)\bar{M}(s,t_0)
\end{equation}
Now, from (\ref{ca_general_future}) and (\ref{approximation_clarkocone}) we have the next approximation for the convexity adjustmet for future
\hspace{1cm}
\fboxsep1em
\fbox{\parbox{435pt}
{
\begin{align}\label{ca_approximation_futures}
CA(t,t_0,t_1)& \nonumber \\ 
\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) \int_{0}^{t_0} \beta(s,t_0,x_0,\hat{y}_s) \nu(s,t_2) ds. 
\end{align}
}}

\begin{example}\label{example_ca_future}
Let us to set 
\begin{align*}
g(T) &= \exp(-kT) \\
h(t) &= \sigma
\end{align*}
\end{example}
With this parametrization, the Cheyette model is equiavalent to Hull-White model. It is easy to show that under this parametrization, the convexity adjustment (\ref{ca_approximation_futures}) is
\begin{align*}
CA(t_0,t_1) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
\end{align*}
In the next figure, we can check the accuracy of the last formula versus montecarlo. The parameters that we have used are $\sigma=0.015$, $k=0.003$ and flat curve with level $r=0.01$.

@@

\subsection{OIS futures}
In this we will derive the covexity adjustment for overnight-indexed swap (OIS) under. We will define for $t_0 < t_1$
\begin{align*}
R(t_0,t_1) &= \frac{\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1}{t_1 - t_0} \\
R_{avg}(t_0,t_1) &= \frac{\int_{t_0}^{t_1}r_{ois,u} du}{t_1 - t_0}.
\end{align*}
We must observe, that both $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictible and they are only observable in $t_1$. However, since
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$, we can considerer the expected value under the measure $\mathbb{Q}^{t_1}$ that will observable during whole period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales  
\begin{align*} 
\bar{R}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R(t_0,t_1)  \right) \\
\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
\end{align*}
We must do several obeservations. The first observation is that
\begin{align*}
F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1}{t_1 - t_0}, \quad t \in [0,t_0] \\
F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{1}{t_1 - t_0} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
\end{align*}
The can define the convexity adjustment for $ R(t_0,t_1)$ the next way
\begin{equation}\label{R_ois_ca}
CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1) 
\end{equation}
The second observation, is that under the dyam we must do is that
\begin{equation}\label{R_ois_avg}
\mathbb{E}_{t}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}_t^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  
\end{equation}
In order to compute $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1\right)$, we will define
\begin{equation*}
I(t_0,t_1) = \int_{t_0}^{t_1} r_s ds
\end{equation*}
then for $t < t_0$ from (\ref{clark-okone}) and (\ref{approximation_D_s_x_t}), we have the next representation for $I(t_0,t_1)$
\begin{align}\label{apprx_I_t0_t1}
I(t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) \bar{M}(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
&\approx \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\hat{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
&= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1} g(s)h(s,x_0,\hat{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
\end{align}
Therefore, we can get the next approximation
\begin{align*}
1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}^{t_1}}\left(R(t_0,t_1)\right) &= \mathbb{E}^{\mathbb{Q}^{t_1}}\left( \exp(I(t_0,t_1)) \right)\\
&= \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)  \mathbb{E}^{\mathbb{Q}^{t_1}}\left(\exp\left(\int_{0}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right)
\end{align*}
where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,\hat{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$. Now, from the Girsanov's theorem we get that
\begin{equation*}
1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{0}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right)
\end{equation*}
Therefore we have that

@@

\subsection{FRAs in arrears}
The cash flows associated to a FRAs in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$. Therefore the payment will be
\begin{equation}
P_{E}(0,t_1)\mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}(t_1,t_1,t_2\right).
\end{equation}
The expected value is clearly taken with respect to the wrong martingale, because $L_{E}(t,t_1,t_2)$ is martingale under the measure $\mathbb{Q}^{t_2}$. In order to calculate, the convexity adjustment we will use as before Clark-Ocone to get a representation for $L_{E}(t_1,t_1,t_2)$ i.e
\begin{equation}\label{general_convexity_fras}
L_{E}(t_1,t_1,t_2) = \mathbb{E}^{\mathbb{Q}^{t_2}}\left(L_{E}(t_1,t_1,t_2) \right) + \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}
\end{equation}
The if we suppose the HJM dynamic (\ref{estimation_forward_rate_curve})and we take $\mathbb{E}^{^{\mathbb{Q}^{t_1}}}(\cdot)$ we get
\begin{align*}
\mathbb{E}^{\mathbb{Q}^{t_1}}\left(L_{E}(t_1,t_1,t_2) \right) &= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}\right)\\
&= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) (\nu(s,t_2)-\nu(s,t_1)) ds \right)
\end{align*}
Where we have used that 
\begin{equation*}
dW^{\mathbb{Q}^{t_2}}_s = dW^{\mathbb{Q}^{t_1}}_s + (\nu(s,t_2) - \nu(s,t_1)) ds 
\end{equation*}
Now from (\ref{approximation_D_s_x_t}) we have that 
\begin{equation*}
D_s L(t_1,t_1,t_2) = \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1} \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, x_0, \bar{y}_s)\bar{M}(s,t_1)
\end{equation*}
Therefore, if we define and we use (\ref{approsimation_E_s_x_t}) we have that
\begin{equation*}
CA(t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}\left(t_1,t_1,t_2\right)\right) - L_{E}\left(0,t_1,t_2\right)
\end{equation*}
and we use the last approximation and (\ref{general_convexity_fras}), we can get the next approximation for $CA(t_0,t_1)$ 
\hspace{2cm}
\fboxsep1em
\fbox{\parbox{475pt}
{
\begin{equation}\label{ca_approximations_fra_arrears}
CA(t_0,t_1) \approx  \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \int_{0}^{t_1} \beta(s,t_1, x_0, \bar{y}_s) \exp\left(-\int_{s}^{t_1} \partial_x \beta(u,t_1,x_0,y_0) \nu(u,t_2) du \right) (\nu(s,t_2) - \nu(s,t_1)) ds.
\end{equation}
}}
\begin{example}
To check how works the last approximation. We will restrict a Hull-White model with mean reversion and volatility constant. We will use are $\sigma=0.1$, $k=0.007$ for our model. The analytical approximation that we get from (\ref{ca_approximation_futures}) is
\begin{equation*}
CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \exp(- k(t_1 + u)) -   \exp(- k(t_2 + u)) du 
\end{equation*}
We have checked the last approximation using MC method to compute the value of a FRA in arrears. We will show the result of the simulation in the next figure
